Pteropod physiological analysis

### 2018-03-24 figures.Rmd
all table sdone

knitr::kable(biotab)
```

>>>>

knitr::kable(biotab, caption = "Table 1: Model results for pteropod cellular response to pairs of co-occurring environmental variables. The estimated joint effects of variables in each model are shown.  The overall R-squred value for each model is also shown.  Significance of each effect is noted as * p < 0.05, ** p < 0.005.")
```

```{r}
phytab <- mods$phy %>% 
  left_join(phymod, by = 'Model') %>% 
  select(Model, data) %>%
  mutate(data = map(data, function(x){
    x %>% mutate(vr = seq(1:nrow(.)))
  })) %>% 
  unnest %>% 
  mutate(
    Model = gsub('mod', '', Model),
    Model = as.numeric(Model)
  ) %>% 
  group_by(Model) %>% 
  mutate(
    Pvl = gsub('ns', '', Pvl), 
    Rsq = ifelse(duplicated(Rsq), '', Rsq)
  ) %>% 
  ungroup %>% 
  unite('Est', Est, Pvl, sep = '') %>% 
  gather('estnm', 'estvl', Rsq, Est) %>% 
  unite('est', pte_lab, estnm, sep = ', ', remove = F) %>% 
  select(-estnm) %>% 
  split(.$pte_lab) %>%
  lapply(., function(x){

    if(!any(grepl('^abu', names(out))))
      out <- out %>% 
        select(-env_lab)

names(phytab) <- gsub('^.*\\.', '', names(phytab))
vrs <- gsub('(^.*),\\s.*$', '\\1', names(phytab))
vrs[duplicated(vrs)] <- ''
vrs <- paste0(vrs, '<br>')
vrs[vrs %in% 'env_lab<br>'] <- 'Parameter<br>'
vrs2 <- gsub('^.*,\\s|Model|env_lab', '', names(phytab))
vrs <- paste(vrs, vrs2, sep = '')
vrs <- gsub('abu', 'Abundance', vrs)
vrs <- gsub('len', 'Length', vrs)
vrs <- gsub('dis', 'Shell dissolution', vrs)

names(phytab) <- vrs

knitr::kable(phytab, caption = "Table 2: Model results for pteropod physiological and population response to pairs of co-occurring environmental variables. The estimated joint effects of variables in each model are shown.  The overall R-squred value for each model is also shown.  Significance of each effect is noted as * p < 0.05, ** p < 0.005.")
```
